Reply to reviewers

### 2025-01-03 review/reply.Rmd
finished changes requested from me

We thank the reviewers for their feedback on the paper. Since the article was submitted as a *short technical note* it is not possible to accomodate all suggestions.

@@

\textcolor{purple}{A comprehensive review would be beyond the scope of a short technical note, but we added additional context XXXX do this? how?}

@@

\textcolor{purple}{To the best of our knowledge, the proposed method is the first that allows the comparison of a reference normal distribution to observations using projection pursuit.}

@@

\textcolor{purple}{The second example in the paper is using real-world data, adding more examples would be beyond the scope of a short technical note.}

@@

\textcolor{purple}{The description is brief, fitting the style of a short technical note. XXX check where we could be more clear...}

@@

\textcolor{purple}{XXX (Need to finish, add references) We have added a paragraph in the introduction discussing outlier detection with other projection pursuit index functions, including the most important references.}

@@

\textcolor{purple}{XXX I think the answer should be no, there is no comparison? Only rescaling for fitting into the plotting window which would be applied to both the nex points and the ellipsoid?}

@@

\textcolor{purple}{XXX todo @Di}

@@

\textcolor{purple}{XXX todo @Di}

@@

\textcolor{purple}{XXX todo @Di}

>>>>

We thank the Associate editor and anonymous reviewers for the feedback on the paper. In discussion with the editor, it is agreed that becuase the article was submitted as a *short technical note* that the revision would focus on these changes only:

1. Make all the small corrections listed by Reviewer 2.
2. Check the computational details to ensure that it is clear.
3. Check the literature references, to ensure nothing major is missed. The reviewers didn’t suggest articles that we had missed citing. We can try to make the context clearer.
4. Ignore the request for a broader comparison or add more examples. The two examples provided are contemporary and differ in nature, illustrating general usage.

@@

\textcolor{purple}{The introduction was slightly expanded, and two new references added to provide additional context.}

@@

\textcolor{purple}{This is first work that allows the comparison of a reference normal distribution to observations using projection pursuit, and a projection pursuit guided tour. New text in the introduction helps clarify this.}

@@

\textcolor{purple}{The two examples used in the paper illustrate different uses of this work in practical settings. The first example uses simulated data for privacy purposes but the data reflects patterns seen in clinical data. The text has been modified to make this clear. There is no room in a short technical report to add more examples.}

@@

\textcolor{purple}{The introduction has been expanded slightly with two more references added to provide more context. XXX check where we could be more clear...}

@@

\textcolor{purple}{Done}

@@

\textcolor{purple}{The new data needs to be pre-processed in the same manner as the reference distribution. For example, if the reference distribution is scaled using means and standard deviations of historical data, these same means and standard deviations need to be used to scale the new data.  XXX Add some sentences to make this clear in the paper}

@@

\textcolor{purple}{The text in section 2 has been changed to remove any specialist language. The explanation is also more detailed now.}

@@

\textcolor{purple}{This figure has been modified to make it clearer, and to correspond with the changed text in the section.}

@@

\textcolor{purple}{Done}
